---
title: "Assement 1"
author: Jing Yong Tan
output: html_document
date: '2022-03-06'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# RMarkdown editing

## RMarkdown

*R Markdown* is a file format for making dynamic documents with R. An *R Markdown* document is written in markdown **an easy-to-write plain text format** and **contains chunks of embedded R code.** [here](https://rmarkdown.rstudio.com/lesson-8.html) 


```{r}
library(tidyverse)
library(knitr)
library(skimr)
library(ggplot2)
```

```{r}
fastfood <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
```

```{r}
fastfood %>% head(10)
```
```{r}
knitr::kable(fastfood[1:10, 1:5])
```
```{r}
fastfood %>%
  filter(calories > 1000)
```

```{r}
dont_eat_this <- fastfood %>%
  filter(total_fat > 40 & total_carb > 80) %>%
  arrange(desc(total_fat), .by_group = TRUE)
head(dont_eat_this)
  
```
```{r}
heavy_food <- fastfood %>%
  mutate(
    type = case_when(
    calories > 500 ~ "heavy",
    calories < 250 ~ "Low",
    TRUE ~ "average"
  )
  ) %>%
  count(type)
```

```{r}
fastfood %>% skim()
```

```{r}
fastfood %>%
  count(restaurant)%>%
  arrange(desc(n),.by_group = TRUE)
```

```{r}
fastfood %>%
  group_by(restaurant) %>%
  summarize(average_cal = mean(calories))
```
```{r}
average_calories<-fastfood %>%
  group_by(restaurant) %>%
  mutate(average_calories = mean(calories)) %>%
  ungroup()
```
```{r}
max_fat<-fastfood %>%
  group_by(restaurant) %>%
  summarise(max_fat = max(total_fat)) %>%
  ungroup()
```
```{r}
min_cholesterol<-fastfood %>%
  group_by(restaurant) %>%
  summarise(min_cholesterol = min(cholesterol)) %>%
  ungroup()
```
```{r}
fastfood %>%
  ggplot(aes(restaurant,total_fat, fill=restaurant))+
  geom_col()
```

#### i think this column chart is the best, it represent by using X and represent the numerical or (total_fat) by using Y. THis chart is easy to read and understand.

```{r}
cholesterol_sodium<-fastfood %>%
  group_by(restaurant) %>%
  summarise(cholesterol_sodium = sum(cholesterol , sodium)) %>%
  ungroup()
```

```{r}
fastfood %>%
  filter(restaurant == 'Mcdonalds') %>%
  ggplot(.,aes(sugar,protein))+
  geom_point()
```
```{r}
fastfood$restaurant<-as_factor(fastfood$restaurant)
class(fastfood$restaurant)
```
```{r}
fastfood<-fastfood %>%
  mutate(calories_type = cut_number(fastfood$calories, 3, labels = c("low", "med","high")))
```
```{r}
fastfood %>% 
  count(restaurant, calories_type, sort=TRUE) %>% 
  ggplot(aes(n,calories_type,fill=factor(calories_type))) +
  geom_col() +
  coord_flip() +
  facet_wrap(~restaurant) +
  theme_linedraw()
```
```{r}
fastfood<-fastfood%>%
  mutate(trans_fat_percent = round (fastfood$trans_fat/fastfood$total_fat*100,2))
```

```{r}
fastfood%>%
  ggplot(aes(restaurant, trans_fat, color=restaurant, fill=restaurant)) + 
  geom_point(alpha=0.4, position="jitter")
```
```{r}
fastfood %>%
  group_by(restaurant) %>%
  summarise(average_fat = mean(total_fat))
```
```{r}
fastfood%>%
  ggplot(aes(restaurant, total_fat,fill=restaurant)) +
  geom_boxplot()
```



